Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores II. Nanoflare Trains

### 2016-06-27 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex

	\par\citet{brosius_pervasive_2014}, using observations of an active region from the EUNIS-13 sounding rocket, found that the intensity ratio of Fe XIX (formed at $T\approx10^{6.95}$ K) to Fe XII (formed at $T\approx10^{6.2}$ K) is $\sim0.59$ inside the AR core as compared to $\sim0.076$ outside, providing possible evidence for impulsive heating. As a proxy for this intensity ratio and an alternative to the hot emission measure slope $b$, we propose using an emission measure ratio, $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$. Unlike an emission measure slope, a simple emission measure ratio gives information about the emission at only a single ``hot'' temperature relative to the cool side. Here, we choose $T_{hot}=10^{6.95}$ K and $T_{cool}=10^{6.3}\approx2\times10^6$ K, the latter slightly higher than the formation temperature of Fe XII such that the emission measure ratio is less sensitive to variations in the cool emission and thus a more accurate measure of the amount of hot plasma. 

@@

	\par The emission measure ratio provides a way to compactly compare every point in our multidimensional parameter space while acknowledging that we are reducing $8\times10^4$ s of loop evolution to a single value. The left panel of \autoref{fig:em_ratio_hist_el} shows the case in which only the electrons are heated, where each individual histogram (denoted by linestyle and color) corresponds to a different type of heating function. This means, for example, that the solid blue histogram includes emission measure ratios for all values of $t_N$, but for only those cases where heating events are chosen from a power-law distribution of $\alpha=-1.5$. We see that the emission measure ratio is largely insensitive to $\alpha$ and is peaked sharply at approximately $0.25$; the distribution peaks at slightly higher values for the $\beta=1$ case though the overall shape of the distribution is the same. Here we have not included the uniform heating case due to small number statistics (i.e. $<20$ emssion measure ratios). The right panel of \autoref{fig:em_ratio_hist_el} shows these same emission measure ratios, but now separated by $t_N$. For example, the solid red histogram includes emission measure ratios for every type of heating function (i.e. uniform, all $\alpha$ and all $\beta$), but for only those runs where $t_N=3000$ s. Note that we choose to only show results for five values of $t_N$ for aesthetic purposes. We find that for $t_N\le3000$ s, the emission measure ratios are largely clustered below 0.5, with $t_N=2000,3000,4000$ s peaking between $\sim0.3-0.45$. It seems that the value of the emission measure ratio is more sensitive to the heating frequency for $t_N>4000$ s.

@@

	\par Similarly, we compute this same emission measure ratio for the case in which only the ions are heated. The left panel of \autoref{fig:em_ratio_hist_ion} shows histograms for each type of heating function. Similar to the electron heating results, we find that the $\beta=0$ distributions peak at lower values compared to the $\beta=1$ distributions and that in the $\beta=0$ case, the distribution of emission measures ratios is relatively insensitive to $\alpha$. However, unlike the electron heating case, the distributions in all cases are much wider and peak at higher values, $\sim0.5$ for $\beta=0$ and $>1$ for $\beta=1$. Furthermore, in the $\beta=1$ case, the $\alpha=-2.5$ distribution peaks at lower values compared $\alpha=-1.5,-2.0$. The right panel of \autoref{fig:em_ratio_hist_ion} shows the same emission measure ratios now grouped by waiting time where again we only show five values of $t_N$. With the exception of the $t_N=2000$ s and $t_N=3000 s$ group, the distributions for each value of $t_N$ are much more spread out (as compared \autoref{fig:em_ratio_hist_el}). In particular, $t_N=5000$ s peaks above 1.0 and extends past 1.5 while $t_N=1000$ peaks near 0 and drops off very steeply before 0.5. In general, the emission measure ratio appears to be more sensitive to $t_N$ compared to the electron heating case.

>>>>

	\par\citet{brosius_pervasive_2014}, using observations of an active region from the EUNIS-13 sounding rocket, found that the intensity ratio of Fe XIX (formed at $T\approx10^{6.95}$ K) to Fe XII (formed at $T\approx10^{6.2}$ K) is $\sim0.59$ inside the AR core as compared to $\sim0.076$ outside, providing possible evidence for impulsive heating. As a proxy for this intensity ratio and an alternative to the hot emission measure slope $b$, we propose using an emission measure ratio, $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$. Unlike an emission measure slope, a simple emission measure ratio gives information about the emission at only a single ``hot'' temperature relative to the cool side. Here, we choose $T_{hot}=10^{6.95}$ K and $T_{cool}=10^{6.3}\approx2\times10^6$ K, the latter slightly higher than the formation temperature of Fe XII such that the emission measure ratio is less sensitive to variations in the cool emission. 

@@

	\par The emission measure ratio provides a way to compactly compare every point in our multidimensional parameter space while acknowledging that we are reducing $8\times10^4$ s of loop evolution to a single value. The left panel of \autoref{fig:em_ratio_hist_el} shows the case in which only the electrons are heated, where each individual histogram (denoted by linestyle and color) corresponds to a different type of heating function. This means, for example, that the solid blue histogram includes emission measure ratios for all values of $t_N$, but only those cases where heating events are chosen from a power-law distribution of $\alpha=-1.5$. We see that the emission measure ratio is largely insensitive to $\alpha$ and is peaked sharply at approximately $0.25$; the distribution peaks at slightly higher values for the $\beta=1$ case though overall shape of the distribution is the same. \hl{Discuss right panel of electron histogram figure}

@@

	\par\hl{Now discuss ion heating results, left and right panels}
